Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow

### 2014-11-25 writeups/dissertation/dissertation.tex
foo

%\documentclass[man,floatsintext,donotrepeattitle]{apa6}
\documentclass[man,donotrepeattitle]{apa6}

@@

Hashtags for Twitter were both placed at the end of the Tweet and embedded within the middle of the tweet.
For the popular-hashtags dataset, 11\% of hashtags were the last word in the Tweet and the rest were embedded within the tweet (not at the end).
Tags for StackOverflow were always placed at the end of the post, since the author chose tags by placing them in a separate text field before submitting the post.

@@

All raw Tweet and post data were stored in Postgres tables.
Also, after the documents were tokenized, the tokenized versions of the raw data were stored in Postgres tables.
When R ran an analysis, it would query the tables to retrieve the correct set of tokenized words and tags.
So there is a lot of R code that uses the RPostgreSQL package to communicate with Postgres as the analysis is running.

>>>>

\documentclass[man,floatsintext,donotrepeattitle]{apa6}
%\documentclass[man,donotrepeattitle]{apa6}

@@

Hashtags for Twitter were both placed at the end of the tweet and embedded within the middle of the tweet.
For the popular-hashtags dataset, 11\% of hashtags were the last word in the tweet and the rest were embedded within the tweet (not at the end).
Tags for StackOverflow were always placed at the end of the post, since the author chose tags by placing them in a separate text field before submitting the post.

@@

All raw tweet and post data were stored in Postgres tables.
Also, after the documents were tokenized, the tokenized versions of the raw data were stored in Postgres tables.
When R ran an analysis, it would query the tables to retrieve the correct set of tokenized words and tags.
So there is a lot of R code that uses the RPostgreSQL package to communicate with Postgres as the analysis is running.
